State and Input Dependent Disturbances in Min-Max Model Predictive Control

### 2016-08-23 notes_c1rhoP.tex
optimization of c1, P, rho

Let $\|x\|=\sqrt{x^T x}$ and let $\|x\|_P=\sqrt{x^T P x}$ for a positive definite matrix $P$. \\
Denote the $P$-ball as $\mathscr B_P(r) = \{x: \|x\|_P \leq r\}$. \\
The Minkowski sum, $\mathcal{X}\oplus\mathcal{Y}$, of sets $\mathcal{X},\mathcal{Y}$ is the set $\{z: \exists (x,y)\in\mathcal{X}\times\mathcal{Y}, z = x+y\}$.

\begin{prop}
The two following equalities hold:
\begin{subequations}\label{eq:balladd}
\begin{equation}
  \mathscr B_P(r_1+r_2) = \mathscr B_P(r_1)\oplus\mathscr B_P(r_2)
\end{equation}
\begin{equation}
  \mathscr B_P(r_1-r_2) = \mathscr B_P(r_1)\ominus\mathscr B_P(r_2) .
\end{equation}
\end{subequations}
\end{prop}

\textit{Proof:}\hspace{1ex}
Let $x_1\in\B_P(r_1)$ and $x_2\in\B_P(r_2)$, then:
\begin{enumerate}[(i).]
\item
the triangle inequality implies $\|x_1+x_2\|_P\leq \|x_1\|_P+\|x_2\|_P$;
%and hence $\B(x_1)\oplus\B_P(x_2) \leq r_1 + r_2$;
\item
choose any $x_1$ such that $\|x_1\|_P = r_1$ and set $x_2 = (r_2/r_1)x_1$ then $\|x_1+x_2\|_P = (1+r_2/r_1)\|x_1\|_P = r_1 + r_2$.
\end{enumerate}
From (i) we have $\B_P(r_1)\oplus\B_P(r_2) \subseteq \B_P(r_1+r_2)$ but (ii) implies $\B_P(r_1)\oplus\B_P(r_2) \supseteq \B_P(r_1+r_2)$ and it follows that $\B_P(r_1) \oplus \B_P(r_2) = \B_P(r_1 + r_2)$.

Define $r_3 = r_1-r_2$ where $r_1\geq r_2 > 0$.
Then $\B_P(r_3 + r_2) = \B_P(r_3) \oplus \B_P(r_2)$ implies $\B_P(r_3) = \B_P(r_3 + r_2) \ominus \B_P(r_2)$, and hence $\B_P(r_1-r_2) = \B_P(r_1) \ominus \B_P(r_2)$.
\mbox{}\hfill$\square$

>>>>

Define $c_1 = c_1(\varrho)$, $P = P(\varrho)$ and 
$\varrho = \arg\max_{r} (1-r) c_1(r)$, where $c_1(r) = 1/\sqrt{t(r)}$ and $t(r)$, $P(r)$ are defined for any given $r\in(\rho(\Psi),1)$ by
\[
\bigl(t(r),P(r)\bigr) 
= \arg\min_{t,P}\ t \ \ \text{subject to} \ \
r^2 P \succ \Psi^T P \Psi \ \ \text{and} \ \
\begin{bmatrix} t & \xi_j^T \\ \xi_j & P\end{bmatrix} \succ 0 \ \forall j\in\mathbb N_r ,
\]
which requires solution of a semidefinite program. The optimal value of $\varrho$ (and hence $c_1(\varrho)$ and $P(\varrho)$) can be determined by performing a line-search over $r\in(\rho(\Psi),1)$ to find the maximizer of $(1-r)c_1(r)$.
%; this requires the solution of a sequence of SDPs.
